\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-27 chapters/3_algorithm.tex
Add descr. of experimental setup

\section{Generalized framework for Signed Graphs Agglomerative Clustering}
In this section we introduce the proposed framework for agglomerative clustering of signed graphs. 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
First, we define the graph notation in Sec. \ref{sec:notation}, then we introduce the generalized algorithm in Sec. \ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms (Sec. \ref{sec:alg_update_rules}).}

@@

\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
\begin{equation}
E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t. clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t. $\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding a clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
\begin{equation}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^1_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as a way to measure how much a clustering is balanced.

@@

\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$. Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
\begin{equation}
  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
\end{equation}
All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes. The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig. \ref{fig:edge_contraction_and_contr_graph}, step b). For basic linkage criteria, e.g. \emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
% As a result, the merged node could be linked to some of its neighbors by double edges . , representing the fact that their interaction should be updated. This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges. 
% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}

\paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}. It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first. It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig. \ref{fig:edge_contraction_and_contr_graph}. 
% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships. 
If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg. \ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
In the Supplementary material we provide a more detailed description of the algorithm and we also comment on its computational complexity (Sec. \ref{sec:complexity}).

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the update rules $f$ tested in this article. Depending on the type of graph (signed or unsigned) and the use of cannot-link constraints, existing and new algorithms are obtained.}
    \label{tab:linkage-criteria}
\end{table*}

@@

In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most used ones. 
Apart from these, for instance, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features. Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

>>>>

\section{Generalized framework for Signed Graphs Agglomerative Clustering}
In this section we introduce the proposed framework for agglomerative clustering of signed graphs. 
%that represents a simple \UPDATE{generalized} formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive node similarities and signed clustering algorithms using attractive and repulsive cues.}\\
First, we define the graph notation in Sec. \ref{sec:notation}, then we introduce the generalized algorithm in Sec. \ref{sec:algorithm} and finally we show \UPDATE{how it can be seen as a generalization of existing and new graph clustering algorithms in Sec. \ref{sec:alg_update_rules}.}

@@

\paragraph{Multicut and correlation clustering} For any clustering $\Pi$ of $\mathcal{G}$, we define as $E^0_\Pi$ the set of edges linking nodes in the same cluster, and as $E_\Pi^1$ the complementary set of edges whose linked nodes belong to distinct clusters:
\begin{equation}
E_\Pi^0 \equiv \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \qquad E^1_\Pi \equiv E \setminus E^0_\Pi.
\end{equation}
% \begin{align}
% E_\Pi^0 &= \{ e_{uv} \in E \,|\, \exists S \in \Pi : u \in S \, \text{and} \, v \in S \}, \\
% E^1_\Pi &= E \setminus E^0_\Pi.
% \end{align}
The set of edges $E_\Pi^1$ is known as the \emph{multicut} of $\mathcal{G}$ w.r.t. clustering $\Pi$. The instance of the NP-hard \emph{weighted correlation clustering} or \emph{minimum cost multicut problem} w.r.t. $\mathcal{G}(V,E,w^+, w^-)$ \cite{kappes2011globally,chopra1991multiway,andres2015lifting} is the task of finding the clustering that optimally balance the attraction and repulsion in the graph and is given by the following optimization problem/binary integer program:
\begin{equation}
% \min_\Pi \texttt{MC}(\Pi) \equiv
 \min_\Pi \sum_{e\in E} \cost_e x_e^\Pi,  \qquad \text{where} \quad x^\Pi_e = 
 \begin{cases} 
 1 & \text{if } e\in E^1_\Pi \\
 0 & \text{otherwise}.
 \end{cases}
\end{equation}
In the next chapters we will use this objective as a way to measure how much a clustering is balanced.

@@

\paragraph{Update rules} During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
An efficient way of implementing these updates can be achieved by representing the agglomeration as a sequence of \emph{edge contractions} in the graph. Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the associated \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, such that $\tilde{V} \subseteq V$ and each node $u\in \tilde{V}$ represents the cluster $S_u \in \Pi$. Edges in $\tilde{E}$ represent adjacency-relationships between clusters and the signed edge weights $\tilde{\cost}_e$ are given by inter-cluster interactions $\tilde{\cost}(e_{uv})=\interact_{S_u,S_v}$. 
For the linkage criteria tested in this work, when two clusters $S_u$ and $S_v$ are merged, the interactions between the new cluster $S_u \cup S_v$ and each of its neighbors depend only on the previous interactions involving $S_u$ and $S_v$. Thus, we can easily recompute these interactions by using a simple \emph{update rule} $f$ that does not involve any loop over the edges of the original graph $\mathcal{G}$. As an example, given the single-linkage criterion defined in Eq. \ref{eq:max_linkage}, the interaction between $S_u \cup S_v$ and one of its neighbors $S_t$ is simply given by:
\begin{equation}
  \interact_{S_u \cup S_v,S_t} = f( \interact_{S_u,S_t}, \interact_{S_v,S_t}) = f(\tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt})) = \max \{ \tilde{\cost}(e_{ut}), \tilde{\cost}(e_{vt}) \}
\end{equation}
All the update rules tested in this article are listed in Table \ref{tab:linkage-criteria}.
% \UPDATE{Every time a pair of clusters is merged, the contracted graph is updated by performing an edge contraction and merging the associated nodes. The only interactions that then need to be updated are those between nodes that after the edge contraction happen to be connected by double edges (see Fig. \ref{fig:edge_contraction_and_contr_graph}, step b). For basic linkage criteria, e.g. \emph{max} or \emph{min}, the new interaction can be formulated in terms of an \emph{update rule} $f$ depending only on the these updates can be computed with an update rule $f$ that depends only on the interactions at the previous step }
% As a result, the merged node could be linked to some of its neighbors by double edges . , representing the fact that their interaction should be updated. This update can be easily achieved by using an \emph{update rule} depending only on the weights of the double edges. 
% \TODO{such a mess...} ...without the need of running a loop over the edges of the original graph.
% \UPDATE{In this way we do not need to recompute the interaction by using the linkage criterion over all the edges of the original graph, that would be computationally expensive.}
\paragraph{The proposed edge contraction algorithm} The proposed generalized Algorithm \ref{main_alg} then proceeds as follows, similarly to the one proposed in \cite{levinkov2017comparative}. It starts with each node assigned to its own cluster and sorts all edges $e\in E$ in a priority queue (PQ) by their absolute weight $|\cost_e|=|w_e^+ - w_e^-|$ in descending order, so that the most attractive and the most repulsive interactions are processed first. It then iteratively pops one edge $e_{uv}$ from PQ and, depending on the priority $\tilde{\cost}$, does the following: in case of attractive interaction $\tilde{\cost}>0$, provided that $e_{uv}$ was not flagged as a cannot-link constraint, then merge the connected clusters, perform an edge contraction of $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and update the priorities of new double edges as explained in Fig. \ref{fig:edge_contraction_and_contr_graph}. 
% For every new pair of double edges in $\tilde{\mathcal{G}}_\Pi$, update their priorities according to one of the update rules listed in Table \ref{tab:linkage-criteria} together with their cannot-link relationships. 
If, on the other hand, the interaction is repulsive ($\tilde{\cost}\leq 0$) and the option \texttt{addCannotLink} of Alg. \ref{main_alg} is \texttt{True}, then the edge $e_{uv}$ is flagged as cannot-link constraint.
In the Supplementary material we provide a more detailed description of the algorithm and we also comment on its computational complexity (Sec. \ref{sec:complexity}).

@@

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the tested update rules $f$. Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}
    \label{tab:linkage-criteria}
\end{table*}

@@

In this work we test and compare the five update rules listed in Table \ref{tab:linkage-criteria} that represents the most common options. 
Apart from these, \cite{nunez2013machine} proposes a learned update rule where a neural network updates the cluster interactions depending on predefined edge and node features. Other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}), whereas 
\cite{funke2018large} uses a \emph{quantile} update rule by populating a histogram for each inter-cluster interaction.

### 2019-04-27 chapters/5_experiments_intro.tex
Polish presentation of different update rules
Add descr. of experimental setup

\subsection{Experimental setup and pixel grid-graph} \label{sec:grid_graph}
\begin{itemize}
\item Define predictions of the classifier (pseudo probabilities) for edge weights
\item Define possible mappings to signed costs
\item Make comment about which version defines nested segmentations and which does not give hirarchical solutions

\end{itemize}

\begin{itemize}
    \item Define long-range grid graph. (Mention the fact of enforcing local merge)
\item Introduce "Poisson" random graph with a given probability of long-range connections
\item Comment about the short- and long-range distinction in the MWS paper? It does not work that well in practice (applying post-processing to remove small segments is easier and better solution).
\item Ad of course we can think about a classifier that separately predict attraction and repulsion
\item Define offset patterns (link to supplementary material), trained networks (loss, etc...) and setups on cremi and cityscapes 
\item Mention postprocessing step: get rid of tiny segments; on CREMI we use watershed to fill the deleted parts 
\end{itemize}

>>>>

\subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pixel and one of its neighbors to belong to the same neuron segment. The affinities do not have to be limited to direct neighboring pixels, in fact, \cite{lee2017superhuman} have shown that using long-range affinities is beneficial for the training of the CNN. Similarly to \cite{wolf2018mutex}, we then train a CNN to predict short- and long-range affinities and use them as input weights for \algname{}. The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. In the Supplementary material (Sec. \ref{sec:training_details}) we provide more details on the chosen neighborhood structure, data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.

The output of the CNN can be represented as a \emph{weighted 3D grid graph}, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
The post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

The trained CNN outputs pseudo-probabilities $p:E \rightarrow [0,1]$ that have to be mapped to positive and negative edge weights\footnote{Note that in general attractive and repulsive interactions $w^+$ and $w^-$ can be independently estimated with different classifiers.}. The most common approaches use \emph{additive} \cite{ailon2008aggregating} or \emph{logarithmic} \cite{finkel2008enforcing,andres2012globally} mappings:
\begin{equation}
\cost_{e,\mathrm{Add}} = p_e - \beta, \qquad \quad \cost_{e,\mathrm{Log}} = \log \left( \frac{p_e}{1-p_e} \right) + \log \left( \frac{\beta}{1-\beta} \right),
\end{equation}
where $\beta \in [0,1]$ is a \emph{bias} parameter that allow a tuning between over- and under-segmentation. We evaluated both of them empirically with each of the tested update rules and found that the additive mapping is the best option in all cases apart from the sum update rule.
